Holomorphic field theories and higher algebra

### 2022-09-20 draft.tex
small changes in SD sec

One appealing aspect of Eager's conjecture is that it is mathematically precise:
duality would mean giving an equivalence of factorization algebras.
It is analogous to claiming that two vertex algebras are equivalent,
such as in the well-known boson-fermion correspondence.
In this sense it is a target at which a mathematician can aim,
rather than the more amorphous statements of duality that one often finds in the physics literature.
In that literature, however, there is guidance on what map of factorization algebras provides the equivalence,
which we describe in the next section.

@@

\owen{new version}

@@

Now such a field theory $\cT$ on $\RR^n$ has a space of solutions $\Sol_\cT(\RR^n)$ to its equations of motion.
A {\em classical vacuum} for the theory is a solution that this translation-invariant,
i.e., a constant solution.
As the solutions $\Sol(\RR^n)$ is a derived stack (at least if you adhere to the perspective we've advocated here), there is a derived stack of classical vacua
\[
\cM_{\rm vac}(\cT) = \Sol_\cT(\RR^n)^{\RR^n}
\]
given by the substack of constant solutions.
We call it the {\em moduli stack of classical vacua} for the theory~$\cT$.

@@

In studying questions about the classical vacua of supersymmetric field theories, however, physicists have not typically worked with the {\em stack}.
Instead, they have worked with a GIT quotient.
For instance, in the setting of a gauge theory with stack $V/G$ of classical vacua, it means they work with
\[
V\Sslash G = \Spec(\cO(V)^G),
\]
the scheme whose ring of functions are the $G$-invariant functions on the representation~$V$.
This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
We will call it the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
(Note that the font of M changes between stack and space.)

@@

For the holomorphic QCD theory \owen{write data} the moduli stack of classical vacua is \owen{write it}
The moduli space is a well-known variety
\[
M_{\rm vac}(\cT) \cong \Gr(N_f, N_c)
\]
by using classical invariant theory. \owen{show?}
A similar computation on the putative dual shows the following.

@@

This relationship, which holds already for the supersymmetric theory before twisting, was one of the original pieces of evidence offered by Seiberg for his duality.

\owen{Sketch proof}: This is the first and second fundamental theorem of classical invariant theory!

>>>>

One appealing aspect of Eager's conjecture is that it is mathematically precise:
duality would mean giving an equivalence of factorization algebras.
It is analogous to claiming that two vertex algebras are equivalent,
such as in the well-known boson-fermion correspondence or in the correspondence between the chiral rings of the A- and B-models of mirror symmetry.
In this sense it is a target at which a mathematician can aim,
rather than the more amorphous statements of duality that one often finds in the physics literature.
In that literature, however, there is guidance on what map of factorization algebras provides the equivalence,
which we describe in the next section.

@@

@@

Now such a field theory $\cT$ on $\RR^n$ has a space of solutions $\Sol_\cT(\RR^n)$ to its equations of motion.
A {\em classical vacuum} for the theory is a solution that is translation-invariant,
i.e., a constant solution.
As the solutions $\Sol(\RR^n)$ is a derived stack (at least if you adhere to the perspective we've advocated here), there is a derived stack of classical vacua
\[
\cM_{\rm vac}(\cT) = \Sol_\cT(\RR^n)^{\RR^n}
\]
given by the substack of constant solutions.
We call it the {\em moduli stack of classical vacua} for the theory~$\cT$.

@@

In studying questions about the classical vacua of supersymmetric field theories, however, physicists have not typically worked with the {\em stack}.
Instead, they have worked with a GIT quotient.
For instance, in the setting of a gauge theory with moduli stack of classical vacua $V/G$, it means they work with
\[
V\Sslash G = \Spec(\cO(V)^G),
\]
the scheme whose ring of functions are the $G$-invariant functions on the representation~$V$.
This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
In practice physicists work ordinary schemes (i.e., without any derived directions), although one can also study the derived affine scheme that is the best approximation to a derived stack.
We will call this GIT quotient the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
(Note that the font of M changes between stack and space.)

@@

For the holomorphic QCD theory $\cT(F,N)$ without mesons, 
the moduli stack of classical vacua is 
\[
\cM_{\rm vac} \cong T^*[1] \left(V_Q \oplus V_Q^*)/SL(N)\right).
\]
By contrast the moduli space is a well-known variety, 
\[
M_{\rm vac}(\cT) \cong \Gr(F, N),
\]
the affine cone of a Grassmannian \owen{under Pl\"ucker embedding? need to check.} 
This result follows from classical invariant theory.
(The quark part of a vacuum lies on an $SL(N)$-orbit of $V_Q$, which consists of $F$ copies of the fundamental representation $\CC^N$, and likewise for the antiquark part.
Identifying the $SL(N)$-invariant functions on $V_Q \oplus V^*_Q$ is one of the fundamental theorems of classical invariant theory.)
The moduli space for the magnetic theory is a bit more complicated but follows from invariant theory as well.

@@

One sees the need for the superpotential in order to obtain this result;
the mesons are added to remember nontrivial relations.
This relationship, which holds already for the supersymmetric theory before twisting, was one of the original pieces of evidence offered by Seiberg for his duality.
